Evaluating Deep Learning Methods for Tokenization of Space-less texts in Old French

### 2019-06-03 article/article.tex
First draft of the article

\documentclass{jdmdh}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{pgfplots}

@@

% To Read : Stutzmann article.
% Parler plus de la variation orthographique de langue

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{4-lines-p0215.png}

@@

\begin{table}
\centering
\begin{tabular}{@{}ll@{}}
\hline
                       & \textbf{Sample}           \\  \hline
\textbf{Input  String} & \texttt{Ladamehaitees'enparti}     \\
\textbf{Mask   String} & \texttt{xSxxxSxxxxxSxxxSxxxxS}     \\
\textbf{Output String} & \texttt{La dame haitee s'en parti} \\ \hline
\end{tabular}
  \caption{Input, mask and human-readable output generated by the model. x are WC and S are WB}
  \label{lst:input_output_example}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{carbon.png}
  \caption{Different possibilities of pre-processing. The option with join=False was kept, as it keeps abbreviation marked as single characters. Note how \texttt{unidecode} loses the P WITH BAR}
  \label{fig:normalization}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{length.png}
  \caption{Distribution of word size over the train, dev and test corpora}
  \label{fig:word_sizes}
\end{figure}

\begin{table}
\begin{tabular}{llll}
\hline
                                                   & Train dataset & Dev dataset & Test dataset \\ \hline
TIRONIAN SIGN ET                                   & 4367          & 541         & 539          \\
CON                             & 508           & 70          & 76           \\
P WITH STROKE THROUGH DESCENDER & 580           & 69          & 84           \\ \hline
\end{tabular}
  \caption{Examples of some MUFI characters distributions}
  \label{tab:mufi_examples}
\end{table}

@@

\begin{figure}
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
          width=\linewidth, % Scale the plot to \linewidth
          grid=major,
          grid style={dashed,gray!30},
          xlabel=Epoch, % Set the labels
          ylabel=Accuracy,
          legend style={at={(0.5,-0.2)},anchor=north},
          x tick label style={rotate=90,anchor=east}
        ]
        \addplot table[x=Epoch,y=CNN 1,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN L,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN w/o P,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN N,col sep=comma] {accuracies.csv};
        \addplot table[x=Epoch,y=CNN L N,col sep=comma] {accuracies.csv};
        \legend{CNN, CNN L, CNN P, CNN N, CNN L N}
      \end{axis}
    \end{tikzpicture}
    \caption{Training Loss (Cross-entropy) until plateau was reached. N = normalized, L = Lower, P = no position embedding. LSTM was removed as it did not go below 0.65}
  \label{fig:loss}
  \end{center}
\end{figure}

\begin{table}
\centering
\begin{tabular}{lllll}
\hline
Model   & Accuracy & Precision & Recall & FScore \\ \hline
CNN     & 0.991    & 0.985     & 0.990  & 0.987  \\
CNN L   & 0.991    & 0.979     & 0.990  & 0.985  \\
CNN P   & \textbf{0.993}    & \textbf{0.990}& \textbf{0.991}  & \textbf{0.990}  \\
CNN N   & 0.991    & 0.987     & 0.988  & 0.988  \\
CNN L N & 0.992    & 0.988     & 0.989  & 0.988  \\
LSTM    & 0.741    & 0.184     & 0.500  & 0.269  \\ \hline
\end{tabular}
\caption{Scores over the test dataset. N = normalized, L = Lower, P = no position embedding.}
\label{tab:scores}
\end{table}

@@

The following inputs has been tagged with the CNN P model. Batch are constructed around the regex \texttt{\\W} with package \texttt{regex}. This explains why inputs such as \texttt{".i."} are automatically tagged as \texttt{" . i . "} by the tool. The input was stripped of its spaces before tagging, we only show the ground truth by commodity.

\begin{itemize}
    \item \texttt{Truth :} Aies joie et leesce en ton cuer car tu auras une fille qui aura .i. fil qui sera de molt grant merite devant Dieu et de grant los entre les homes.
    \item \texttt{Input :} Aiesjoieetleesceentoncuercartuaurasunefillequiaura.i.filquiserademoltgrantmeritedevantDieuetdegrantlosentreleshomes.
    \item \texttt{CNN :} Aiesjoie et leesce en ton cuer car tu auras une fille qui aura . i . fil qui sera de molt grant merite devant Dieu et de grant los entre les homes .
    \item \texttt{CNN lower:}	Aies joie et leesce en ton cuer car tu auras une fille qui aura . i . fil qui sera de molt grant merite devant Dieu et de grant los entre les homes .
    \item \texttt{CNN without position:} Aiesjoie et leesce en ton cuer car tu auras une fille qui aura . i . fil qui sera de molt grant merite devant Dieu et de grant los entre les homes .
    \item \texttt{CNN Normalize:}	Aies joie et leesce en ton cuer car tu auras une fille qui aura . i . fil qui sera de molt grant merite devant Dieu et de grant los entre les homes .
\end{itemize}

@@

We believe that, aside from a graphical challenge, word segmentation in OCR from manuscripts can actually be treated from a text point of view

% "The purpose of the discussion is to interpret and describe the significance of your findings in light of what was already known about the research problem being investigated and to explain any new understanding or insights that emerged as a result of your study of the problem. The discussion will always connect to the introduction by way of the research questions or hypotheses you posed and the literature you reviewed, but the discussion does not simply repeat or rearrange the first parts of your paper; the discussion clearly explain how your study advanced the reader's understanding of the research problem from where you left them at the end of your review of prior research."

@@

While
% The conclusion is intended to help the reader understand why your research should matter to them after they have finished reading the paper. A conclusion is not merely a summary of the main topics covered or a re-statement of your research problem, but a synthesis of key points and, if applicable, where you recommend new areas for future research. For most college-level research papers, one or two well-developed paragraphs is sufficient for a conclusion, although in some cases, three or more paragraphs may be required.

\subsection{Acknowledgement}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{confusion.png}
  \caption{Confusion matrix of the CNN model without position embedding}
  \label{fig:confusion_matrix}
\end{figure}

\section{Annex 2}
Cras tristique vel nisi at aliquet. Proin egestas erat sit amet velit lobortis imperdiet. Integer et arcu sapien. Etiam id blandit
sapien. Nam tempus lacus ac massa semper, vel laoreet turpis rutrum. Mauris eget nibh vitae justo porta imperdiet sed vel
ligula. In imperdiet, augue vel condimentum convallis, neque augue imperdiet neque, eget dapibus nunc mauris ultricies
tortor. Nam eget nunc egestas, blandit lectus non, aliquam nunc. Cras sed quam vitae arcu ornare lobortis. Ut ut lacus
hendrerit, convallis orci sit amet, commodo nunc. Pellentesque eget tincidunt tortor. Nunc ornare molestie mauris id vehicula.
Suspendisse pharetra tortor metus, sit amet fermentum tellus vehicula ut.

>>>>

\documentclass{jdmdh}
\usepackage[utf8]{inputenc}
\usepackage{array}
\usepackage{pgfplots}
\usepackage{tabularx}
\newcolumntype{C}{>{\arraybackslash}X} % centered "X" column

@@

% To Read : Stutzmann article.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\linewidth]{4-lines-p0215.png}

@@

\begin{table}[!ht]
\centering
\begin{tabular}{@{}ll@{}}
\hline
                       & \textbf{Sample}           \\  \hline
\textbf{Input  String} & \texttt{Ladamehaitees'enparti}     \\
\textbf{Mask   String} & \texttt{xSxxxSxxxxxSxxxSxxxxS}     \\
\textbf{Output String} & \texttt{La dame haitee s'en parti} \\ \hline
\end{tabular}
  \caption{Input, mask and human-readable output generated by the model. x are WC and S are WB}
  \label{lst:input_output_example}
\end{table}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\linewidth]{carbon.png}
  \caption{Different possibilities of pre-processing. The option with join=False was kept, as it keeps abbreviation marked as single characters. Note how \texttt{unidecode} loses the P WITH BAR}
  \label{fig:normalization}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\linewidth]{length.png}
  \caption{Distribution of word size over the train, dev and test corpora}
  \label{fig:word_sizes}
\end{figure}

\begin{table}[!ht]
\begin{tabular}{llll}
\hline
                                                   & Train dataset & Dev dataset & Test dataset \\ \hline
TIRONIAN SIGN ET                                   & 4367          & 541         & 539          \\
CON                             & 508           & 70          & 76           \\
P WITH STROKE THROUGH DESCENDER & 580           & 69          & 84           \\ \hline
\end{tabular}
  \caption{Examples of some MUFI characters distributions}
  \label{tab:mufi_examples}
\end{table}

@@

\begin{figure}[!ht]
  \begin{center}
    \begin{tikzpicture}
      \begin{axis}[
          width=\linewidth, % Scale the plot to \linewidth
          grid=major, 
          grid style={dashed,gray!30},
          xlabel=Epoch, % Set the labels
          ylabel=Accuracy,
          legend style={at={(0.5,-0.2)},anchor=north},
          x tick label style={rotate=90,anchor=east}
        ]
        \addplot table[x=Epoch,y=CNN 1,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN L,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN w/o P,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN N,col sep=comma] {accuracies.csv}; 
        \addplot table[x=Epoch,y=CNN L N,col sep=comma] {accuracies.csv}; 
        \legend{CNN, CNN L, CNN P, CNN N, CNN L N}
      \end{axis}
    \end{tikzpicture}
    \caption{Training Loss (Cross-entropy) until plateau was reached. N = normalized, L = Lower, P = no position embedding. LSTM was removed as it did not go below 0.65}
  \label{fig:loss}
  \end{center}
\end{figure}

\begin{table}[!ht]
\centering
\begin{tabular}{lllll}
\hline
Model   & Accuracy & Precision & Recall & FScore \\ \hline
CNN     & 0.991    & 0.985     & 0.990  & 0.987  \\
CNN L   & 0.991    & 0.979     & 0.990  & 0.985  \\
CNN P   & \textbf{0.993}    & \textbf{0.990}& \textbf{0.991}  & \textbf{0.990}  \\
CNN N   & 0.991    & 0.987     & 0.988  & 0.988  \\
CNN L N & 0.992    & 0.988     & 0.989  & 0.988  \\
LSTM    & 0.741    & 0.184     & 0.500  & 0.269  \\ \hline
\end{tabular}
\caption{Scores over the test dataset. N = normalized, L = Lower, P = no position embedding.}
\label{tab:scores}
\end{table}

@@

The following inputs has been tagged with the CNN P model. Batch are constructed around the regular expression \texttt{\\W} with package \texttt{regex}. This explains why inputs such as \texttt{".i."} are automatically tagged as \texttt{" . i . "} by the tool. The input was stripped of its spaces before tagging, we only show the ground truth by commodity.

\begin{table}[!ht]
\centering
\begin{tabularx}{\textwidth}{|C|C|}
\hline
\textbf{Ground truth} & \textbf{Tokenized output} \\\hline
Aies joie et leesce en ton cuer car tu auras une fille qui aura .i. fil qui sera de molt grant merite devant Dieu et de grant los entre les homes.Conforte toi et soies liee car tu portes en ton ventre .i. fil qui son lieu aura devant Dieu et qui grant honnor fera a toz ses parenz. & Aies joie et leesce en ton cuer car tu auras une fille qui aura .  i .  fil qui sera de molt grant merite devant Dieu et de grant los entre les homes .  Confort e toi et soies liee car tu portes en ton ventre .  i .  fil qui son lieu aura devant Dieu et qui grant honnor fera a toz ses parenz .
\\\hline
\end{tabularx}
\caption{Output examples on a text from outside the dataset}
\label{tab:example_output}
\end{table}

@@

We believe that, aside from a graphical challenge, word segmentation in OCR from manuscripts can actually be treated from a text point of view and as a NLP task. Word segmentation for some text can be even difficult for humanist, and as such, we believe that post-processing of OCR through tools like Boudams can be a better way to achieve data-mining of the dataset. In light of the high accuracy of the model, we believe the model should perform the same way independently from the language in Medieval Western Europe.

We were surprised by the negligible effects of the different normalization methods (lower-casing; ASCII reduction; both). The presence of certain MUFI characters might provide enough information about segmentation and be in enough numbers for them not to impact the network weights.

@@

Achieving 0.99 accuracy on word segmentation with a corpus as large as 25,000 test samples seems to be the first step for a more important data mining of OCRed manuscript. In aftermath, we wonder if the importance of normalization and lowering should be higher depending on the size of the corpora and its content.

\subsection{Acknowledgements}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\linewidth]{confusion.png}
  \caption{Confusion matrix of the CNN model without position embedding}
  \label{fig:confusion_matrix}
\end{figure}
